A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-07-25 Manuscript/vaught_2017.tex
7/25/18

The mass and energy of galactic winds remain poorly constrained via traditional absorption line studies. One way to better constrain these parameters is to measure the spatial extent of the outflow in emission. We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission. These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).  We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc from the sample galaxies. Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks. Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to model \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds. We find that anisotropic winds reduce the strength of estimated missing \ion{Mg}{2} emission below our 5$\sigma$ limit.

@@

One way of constraining the radial extent and morphology of the outflow is to trace winds in emission. This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) as these transitions can trace the warm shock heated phase of the gas. 
A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet (UV)
(Weiner et al. 2009; Kornei et al. 2013)\nocite{Weiner2009, Kornei2013}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.  This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.

@@

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$. 
%The value in using narrowband imaging is the ability to spatially resolve any absorption and emission from a galaxy. 
We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs.
%The continuum filter allows us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet. With the resulting images taken using the two filters, we can subtract the continuum image from the \ion{Mg}{2} image, effectively creating an image that contains only photons from \ion{Mg}{2}. 
As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind. This narrowband imaging allows us to create the first ever high-S/N spatially resolved map of \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We go into detail in our method of continuum subtraction in Section \ref{sec.cont_sub}. The analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
%in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband %measured equivalent widths. 
Section \ref{sec:results} presents results from our narrowband imaging analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al. 2007)\nocite{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.

@@

FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). The seeing, which ranged from $0.5\arcsec$ to $2.5\arcsec$, are given in the image header and are derived from DIMM seeing measurements. These DIMM values are calculated from zenith observations of bright stars at 0.5 microns, which are then reduced to the zenith angles and wavelengths of the science observation. Additionally, a first order correction is then applied for appropriate for a 8m telescope is applied (see Figure \ref{fig.seeing})  Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.

@@

\subsection{Image Reduction}
The data were reduced using custom routines written in \textbf{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
To improve the flat-fielding essential for detecting faint extended emission across the fields,we further correct for the illumination patterns using night-sky flats. The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L.A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net (Lang et al. 2010)\nocite{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015)\nocite{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are weighted by the night-flat image and then  average-combined  in order to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
%weighting and average-combining the RMS images for individual science frames.
 %from the night flats and the combination of RMS images for individual science frames. 
Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

\begin{table*}[t]
\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were 
determined from analysis of the supplemental Keck/LRIS spectra.}
\begin{tabular}{llllllll} \hline \hline
Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper } & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ 97.5th percentile of the $\tau_V$ distribution}\smallskip      \\ \hline 
J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ & 4.812\\

J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & 3.427\\

J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & 2.867 \\

J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & 5.042\\

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ &4.022 \\

@@

\begin{table}[h!]
\caption{Filter properties  and exposure times of the VLT/FORS2 observations. The width of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curve with the total wavelength range of the filter. These values differ slightly from those reported by the European Space Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$\lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{Total number of images}   & $T(s)$\footnote{Total exposure time} & $S$\footnote{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ }\smallskip  \\ \hline 
HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 & 4722.46  & 44.82 & 38 &   36,937 & 2.40  \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients ($k$) to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. We perform absolute flux calibration using the methods of Jacoby et al. (1990). We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
%However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC). 
However, we calculate the integral numerically.
The system sensitivity, including the defects of the telescope optics and detector response is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

@@

\subsection{Spectral Correction}
In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
We use the supplementary spectra from \citet{Rubin_2014} to fit the continuum and determine the spectral slope of each galaxy. We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package (Prochaska et al. 2016)\footnote{https://github.com/linetools/linetools}\nocite{Prochaska2016} to fit the continuum. We then find the total continuum flux in each filter by convolving the fitted continuum with each filter's transmission curve. Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction. Comparing these ratios between each galaxy, we find that they are effectively the same, within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHM of the filter transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.

@@

\begin{table}[h]
\centering
%\begin{minipage}{4in}
\caption{Significance of extracted flux and detection limits\label{tab:det_lims}}  
\begin{tabular}{lllll} \hline \hline
Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{\ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$. The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$ } & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$} & Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
J033232.36-274725.0 &  -1.40(-0.53)& 6.51 & 21 \\
J033230.03-274347.3 &  -5.23(-1.75)& 5.74 & 27 \\
J033229.64-274242.5 &  1.23 (0.44) & 6.22  &26 \\
J033230.57-274518.2 &  -2.53 (-1.00) & 6.81 &18 \\ \hline
\end{tabular}
%\end{minipage}
\end{table}

@@

\begin{figure*}[p]
\centering
\includegraphics[scale=1.2]{../Figures/sigmas.pdf}
\caption{Postage stamp $\chi_{\text{smooth}}$ images for the Mg II emission of the 5 galaxies in our sample. Every galaxy is placed in the same row in each column. The columns show simulated emission, with levels of 0, 1, 3, 5, 10, and 20 times SB$_{lim}$.  Each postage stamp has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$). Each stamp shows the galaxy along with the same isophotal contour used in previous figures.}
\label{fig:sigmas}
\end{figure*}

@@

To compare our map of EW$_{\rm{MgII}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy. The width and angle of the apertures replicate the orientation of the slits used to obtain the spectra. Next, we determine which pixels lie outside the 1$\sigma$ SB$_1$ contours and set their values to zero. Outside this contour, the EW$_{\rm{MgII}}$ values become poorly constrained due to the lack of S/N in the continuum. We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EW$_{\rm{MgII}}$ inside the contour. The histograms are shown in Figures \ref{fig:ew11} through \ref{fig:ew55}. Having removed pixels with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures. These values are summarized in Table \ref{tab:abs_props}.

>>>>

The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies. One way to better constrain these parameters is to measure the spatial extent of the outflow in emission. We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission. These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).  We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc from the sample galaxies. We do detect significant spatially-resolved \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks. Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds. Based on these comparisons, if our galaxies do host \ion{Mg}{2} emission, then the predicted \ion{Mg}{2} based on this modeling suggests that these winds are anisotropic and dusty for any scattered \ion{Mg}{2} emission to lie below our 5$\sigma$ detection limits.

@@

One way of constraining the radial extent and morphology of the outflow is to trace winds in emission. This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts \citep[][]{{Matsubayashi2009,Veilleux2009,Tripp2011}} as these transitions can trace the warm shock heated phase of the gas. 
A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
\citep[UV,][]{{Weiner2009, Kornei2013}}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.  This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.

@@

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$. 
We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs.

As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind. This narrowband imaging allows us to create the first ever high-S/N spatially resolved map of \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We go into detail in our method of continuum subtraction in Section \ref{sec.cont_sub}. The analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
%in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband %measured equivalent widths. 
Section \ref{sec:results} presents results from our narrowband imaging analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field \citep[the Extended Groth Strip;][]{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.

@@

FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). 
The seeing values, given in the header of each image, are derived from zenith observations at 0.5 microns with the Paranal differential image motion monitor \citep[DIMM,][]{Sarazin1990}. The initial DIMM values are then corrected to the airmass and wavelengths of the science observation. Finally, a first order correction is then applied for appropriate for a 8m telescope is applied (see Figure \ref{fig.seeing}). The median seeing for the images is $\sim 0.8\arcsec$

Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.

@@

\subsection{Image Reduction}
The data were reduced using custom routines written in \emph{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
To improve the flat-fielding essential for detecting faint extended emission across the fields,we further correct for the illumination patterns using night-sky flats. The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L.A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are weighted by the night-flat image and then  average-combined  in order to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
 Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

\begin{table*}[t]
\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were 
determined from analysis of the supplemental Keck/LRIS spectra.}
\begin{tabular}{llllllll} \hline \hline
Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper. } & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust.}\smallskip      \\ \hline 
J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\

J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & $1.377_{-0.23}^{+0.60}$\\

J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\

J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$\\

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\

@@

\begin{table}[h!]
\caption{Filter properties  and exposure times of the VLT/FORS2 observations. The width of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curve with the total wavelength range of the filter. These values differ slightly from those reported by the European Space Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{ Total number of images.}   & $T(s)$\footnote{ Total exposure time.} & $S$\footnote{ S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ .}\smallskip  \\ \hline 
HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 & 4722.46  & 44.82 & 38 &   36,937 & 2.40  \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients, $k$, to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. We perform absolute flux calibration using the methods of \cite{Jacoby1987}. We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
%However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC). 
However, we calculate the integral numerically.
The system sensitivity, including the defects of the telescope optics and detector response is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

@@

\subsection{Spectral Correction}
In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
We use the supplementary spectra from \citet{Rubin_2014} to fit the continuum and determine the spectral slope of each galaxy. We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package \citep{Prochaska2016}\footnote{https://github.com/linetools/linetools} to fit the continuum. We then find the total continuum flux in each filter by convolving the fitted continuum with each filter's transmission curve. Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction. Comparing these ratios between each galaxy, we find that they are effectively the same, within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHM of the filter transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.

@@

\begin{table}[h]
\centering
%\begin{minipage}{4in}
\caption{Significance of extracted flux and detection limits\label{tab:det_lims}}  
\begin{tabular}{lllll} \hline \hline
Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{ \ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$. The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$. } & 5SB$_{\text{limit}}$\footnote{ Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & Area\footnote{ Area of the extended annulus in sq.arcsec.} \\  \hline
J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
J033232.36-274725.0 &  -1.40(-0.53)& 6.51 & 21 \\
J033230.03-274347.3 &  -5.23(-1.75)& 5.74 & 27 \\
J033229.64-274242.5 &  1.23 (0.44) & 6.22  &26 \\
J033230.57-274518.2 &  -2.53 (-1.00) & 6.81 &18 \\ \hline
\end{tabular}
%\end{minipage}
\end{table}

@@

\begin{figure*}[p]
\centering
\includegraphics[scale=1.2]{../Figures/sigmas.pdf}
\caption{Postage stamp $\chi_{\text{smooth}}$ images for the Mg II emission of the 5 galaxies in our sample. Every galaxy is placed in the same row in each column. The columns show simulated emission, with levels of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.  Each postage stamp has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$). Each stamp shows the galaxy along with the same isophotal contour used in previous figures.}
\label{fig:sigmas}
\end{figure*}

@@

To compare our map of EW$_{\rm{MgII}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy. The width and angle of the apertures replicate the orientation of the slits used to obtain the spectra. Next, we determine which pixels lie outside the 1$\sigma$ SB$_1$ contours and set their values to zero. Outside this contour, the EW$_{\rm{MgII}}$ values become poorly constrained due to the lack of S/N in the continuum. We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EW$_{\rm{MgII}}$ inside the contour. The histograms are shown in Figure \ref{fig:ews}. Having removed pixels with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures. These values are summarized in Table \ref{tab:abs_props}.

To assess the morphology of the \ion{Mg}{2} absorption, we determine the distance of each pixel from the center of each galaxy in kiloparsecs. We plot the EW$_{\rm{MgII}}$ over this projected distance for each galaxy in Figure \ref{fig:ews}. Although some of the plots suggest a slight upward trend in the values of the EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter. To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc-wide bins. For example, in Figure \ref{fig:ews}(c), the EW$_{\rm{MgII}}$ from absorption of J.03 extends out to $\sim$ 25 kpc. The EW$_{\rm{MgII}}$ values are binned in 5 kpc increments. We calculate the mean and scatter of the EW$_{\rm{MgII}}$ in each bin and show these values in Figure \ref{fig:ew_comb}.
